Followers Are Not Enough: Beyond Structural Communities in Online Social Networks \\Followers Are Not Enough: A Question-Oriented Approach to Community Detection

### 2014-07-30 paper-for_arxiv/conclusions.tex
fixing influence in conclusion

%Start of future work**
Our findings have important implications to a common problem in social network analysis: identification of influential individuals. Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}. Most centralities depend explicitly on the structure of the network under consideration. But we have seen in our study that a structural network alone is not sufficient to capture user interaction or influence in online social media. Thus, a na\"ive application of centrality measures to a structural network for influence detection may give rise to erroneous results. This result has been explored previously~\cite{kitsak2010identification}, and our work further highlights its importance. We believe that weighted generalizations of these centralities using transfer entropy might lead to better insights about who is actually influential in an online social network. In addition to exploring this phenomenon further, we plan to explore a broader selection of choices for both the transfer-entropy lag and tweet history time resolution. We believe that by doing an in-depth analysis of both of these parameters we can discover interesting activity-based communities that occur on much broader time scales.
%End of futre work**
  %based on methods for model selection~\cite{claeskens2008model}.

@@

This work demonstrates that asking the proper question and then crafting an appropriate weighting scheme to answer that question is an unavoidable first step for community detection in online social media. More generally, this work illustrates that without a clear definition of community, many rich and interesting communities present in online social networks remain invisible. Question-oriented community detection can bring those hidden communities into the light.

>>>>

%Start of future work**
Our findings may have important implications to a common problem in social network analysis: identification of influential individuals---but further work must be carried out. Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}. Most centralities depend explicitly on the structure of the network under consideration. 
But we have seen in our study that a structural network alone is not sufficient to capture user interaction or even activity-based influence in online social media. Thus, a na\"ive application of centrality measures to a structural network for influence detection may give rise to erroneous results. This result has been explored previously~\cite{kitsak2010identification}, and our work further highlights its importance.

Based on our preliminary results, we conjecture that weighted generalizations of these centrality measures using transfer entropy might lead to better insights about who is actually influential in an online social network. In addition to exploring this phenomenon further, we plan to explore a broader selection of choices for both the transfer-entropy lag and tweet history time resolution. We believe that by doing an in-depth analysis of both of these parameters we can discover interesting activity-based communities that occur on much broader time scales.
%End of futre work**
  %based on methods for model selection~\cite{claeskens2008model}.

@@

This work demonstrates that asking the proper question, and then crafting an appropriate weighting scheme to answer that question, is an unavoidable first step for community detection in online social media. More generally, this work illustrates that without a clear definition of community, many rich and interesting communities present in online social networks remain invisible. Question-oriented community detection can bring those hidden communities into the light.
